Road Segment Prioritization for Bicycle Infrastructure

### 2020-11-18 README.Rmd
edited Routing section in paper

The next step is to route the potential cycling demand ($\boldsymbol{C_{p}}$) between all OD pairs onto the road network. **TALK ABOUT WEIGHTED ROUTING IN OTHER STUDIES **
<!-- This expands on the work of @mauttone2017bicycle, by going beyond simply favoring roads with existing cycling infrastructure to creating a hierarchy of road preference. -->

@@

The weighting profiles are therefore adjusted to favor less stressful streets (based on information from Table  \@ref(table:osmroadtypes)), and roads with existing cycling infrastructure. This is also in line with the creation of LTNs, as residential streets are those where motorized traffic is most likely to be banned in the creation of LTNs.

@@

Routing potential cycling demand on a weighted network is more in line with government policy to create LTNs. Figure \@ref(fig:flowsfacetweighted) shows that routing on the weighted network significantly reduces flow on the trunk and primary roads, but does not eliminate it completely. This is intentional, as the impedance on these roads is only slightly higher than remaining road types (See Table \@ref(table:weightprofiles)). Potential cycling demand is only routed on these roads if there are no routes through other roads that offer comparable directness.

@@

Given that cyclists will only deviate from shortest paths by a certain amount to access better cycling infrastructure (as explained in Section \@ref(introduction), allowing flow on some stretches of trunk and primary roads is necessary to insure cycling uptake and equitable access to cycling infrastructure. In its new vision for walking and cycling, the Department for Transport acknowledges that minimal segregated stretches of bicycle lanes on main roads will be necessary to avoid circuitous cycling networks [@departmentgearchange2020].

>>>>

The next step is to route the potential cycling demand ($\boldsymbol{C_{p}}$) between all OD pairs onto the road network. 
<!-- This expands on the work of @mauttone2017bicycle, by going beyond simply favoring roads with existing cycling infrastructure to creating a hierarchy of road preference. -->

@@

The above points are accounted for by using a weighted road network for routing. This has previously been done by multiplying all road segments without cycling infrastructure by an impedance factor [@mauttone2017bicycle], or by assigning a weight to the road segment proportional to the investment cost of bringing it to an acceptable level of stress for cycling  [@duthie2014optimization]. Our approach is similar to the latter, as we create a weighting profile that is adjusted to favor less stressful streets (based on information from Table  \@ref(table:osmroadtypes)), and roads with existing cycling infrastructure. We believe this to be more practical  than the approach adopted by @mauttone2017bicycle, as it goes beyond simply favoring roads with existing cycling infrastructure to creating a hierarchy of road preference based on perceived stress levels. The approach is also in line with the creation of LTNs, as residential streets are those where motorized traffic is most likely to be banned in the creation of LTNs.

@@

Figure \@ref(fig:flowsfacetweighted) shows that routing on the weighted network significantly reduces flow on the trunk and primary roads, but does not eliminate it completely. This is intentional, as the impedance on these roads is only slightly higher than remaining road types (See Table \@ref(table:weightprofiles)). Potential cycling demand is only routed on these roads if there are no routes through other roads that offer comparable directness.

@@

Given that cyclists will only deviate from shortest paths by a certain amount to access better cycling infrastructure (as explained in Section \@ref(introduction)), allowing flow on some stretches of trunk and primary roads is necessary to insure cycling uptake and equitable access to cycling infrastructure. In its new vision for walking and cycling, the Department for Transport acknowledges that minimal segregated stretches of bicycle lanes on main roads will be necessary to avoid circuitous cycling networks [@departmentgearchange2020].
